---
title: "Connectives + QUD Study: Decision RT"
author: Morgan Moyer
date: July 12, 2022
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(stringr)
library(textstem)
library(tidyverse)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
```

```{r set wd and read in all the data, include=FALSE, warning=FALSE, echo=FALSE, message=FALSE}
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")

s <- read.csv("../01_pilot-SpecificQUD/data/processed.csv")
s$QUDType <- "Specific"

g <- read.csv("../02_pilot-GeneralQUD/data/processed.csv")
g$QUDType <- "General"

n <- read.csv("../03_pilot-NoQUD/data/processed.csv")
n$QUDType <- "None"

d <- rbind(s,g,n)
names(d)
d$DecisionRT <- as.numeric(d$DecisionRT)
```

```{r}
names(d)
nrow(d) #1440

length(unique(d$ID)) # 60 --> 48
```

# add the mention/not mention factor
```{r}
d$Mention <- ""
d$Mention[(d$Number == "1") |
            (d$Number == "2") |
            (d$Number == "7") |
            (d$Number == "8")] <- "Mentioned"

d$Mention[(d$Number == "3") |
            (d$Number == "4") |
            (d$Number == "5") |
            (d$Number == "6") |
            (d$Number == "9") |
            (d$Number == "10") |
            (d$Number == "11") |
            (d$Number == "12")] <- "NotMentioned"



d$AnswerQUDRelevant <- ""
d$AnswerQUDRelevant[(d$Number == "1") |
            (d$Number == "2") |
            (d$Number == "11") |
            (d$Number == "12")] <- "NotQUDRelevant"

d$AnswerQUDRelevant[(d$Number == "3") |
            (d$Number == "4") |
            (d$Number == "5") |
            (d$Number == "6") |
            (d$Number == "7") |
            (d$Number == "8") |
            (d$Number == "9") |
            (d$Number == "10")] <- "QUDRelevant"

```


# Denisty

## QUD (raw RT)
```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  # is.numeric(DecisionRT) %>%
  group_by(Letters,Conj,QUDType) %>% #AnswerQUDRelevant,Mention,QUDType
  summarize(meanRT = mean(DecisionRT)) 
  # mutate(YMin = meanLogRT - CILow, YMax = meanLogRT + CIHigh)

ggplot(agr, aes(x = meanRT, fill=Conj, color=Conj)) +
  geom_density(alpha = .4) +
  facet_wrap(~QUDType)
# ggsave("graphs/denisty_QUD_rawRT.pdf",width=7,height=2)

ggplot(agr, aes(x=Conj, y=meanRT,fill=Conj, color=Conj)) + 
  geom_violin(trim=FALSE,alpha=.4) +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  facet_wrap(~QUDType)
```


```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  group_by(QUDType,Conj) %>%
  summarize(meanRT = mean(DecisionRT), CILow = ci.low(DecisionRT), CIHigh = ci.high(DecisionRT)) %>%
  mutate(YMin = meanRT - CILow, YMax = meanRT + CIHigh)

dodge <- position_dodge(.9)
ggplot(agr,aes(x=Conj, y=meanRT, fill=QUDType)) +
  # facet_grid(Mention~AnswerQUDRelevant) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean RT for Decision RT")
```



## QUD x AnswerQUDRelevant (raw RT)
```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  # is.numeric(DecisionRT) %>%
  group_by(Letters,Conj,QUDType,AnswerQUDRelevant) %>% #,Mention
  summarize(meanRT = mean(DecisionRT)) 
  # mutate(YMin = meanLogRT - CILow, YMax = meanLogRT + CIHigh)

ggplot(agr, aes(x = meanRT, fill=Conj, color=Conj)) +
  geom_density(alpha = .4) +
  facet_grid(AnswerQUDRelevant~QUDType)
# ggsave("graphs/denisty_QUDxRelevance_rawRT.pdf",width=6,height=3)

ggplot(agr, aes(x=Conj, y=meanRT,fill=Conj, color=Conj)) + 
  geom_violin(trim=FALSE,alpha=.4) +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  facet_grid(AnswerQUDRelevant~QUDType)
```

```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  group_by(QUDType,Conj,AnswerQUDRelevant) %>%
  summarize(meanRT = mean(DecisionRT), CILow = ci.low(DecisionRT), CIHigh = ci.high(DecisionRT)) %>%
  mutate(YMin = meanRT - CILow, YMax = meanRT + CIHigh)

dodge <- position_dodge(.9)
ggplot(agr,aes(x=Conj, y=meanRT, fill=QUDType)) +
  facet_wrap(~AnswerQUDRelevant) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean RT for Decision RT")
```

## QUD x Mention (raw RT)
```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  # is.numeric(DecisionRT) %>%
  group_by(Letters,Conj,QUDType,Mention) %>% #,Mention
  summarize(meanRT = mean(DecisionRT)) 
  # mutate(YMin = meanLogRT - CILow, YMax = meanLogRT + CIHigh)

ggplot(agr, aes(x = meanRT, fill=Conj, color=Conj)) +
  geom_density(alpha = .4) +
  facet_grid(Mention~QUDType)

# ggsave("graphs/denisty_QUDxMention_rawRT.pdf",width=6,height=3)


# Violn plot
ggplot(agr, aes(x=Conj, y=meanRT,fill=Conj, color=Conj)) + 
  geom_violin(trim=FALSE,alpha=.4) +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  facet_grid(Mention~QUDType)

# ggsave("../graphs/1a_violin.pdf",width=4,height=2)
```


```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  group_by(QUDType,Conj,Mention) %>%
  summarize(meanRT = mean(DecisionRT), CILow = ci.low(DecisionRT), CIHigh = ci.high(DecisionRT)) %>%
  mutate(YMin = meanRT - CILow, YMax = meanRT + CIHigh)

dodge <- position_dodge(.9)
ggplot(agr,aes(x=Conj, y=meanRT, fill=QUDType)) +
  facet_wrap(~Mention) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean RT for Decision RT")
```


## QUD x Mention X AnswerQUDRelevant (raw RT)
```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  # is.numeric(DecisionRT) %>%
  group_by(Letters,Conj,QUDType,Mention,AnswerQUDRelevant) %>% #,Mention
  summarize(meanRT = mean(DecisionRT)) 
  # mutate(YMin = meanLogRT - CILow, YMax = meanLogRT + CIHigh)

ggplot(agr, aes(x = meanRT, fill=Conj, alpha=QUDType, color=Conj)) +
  geom_density(alpha = .4) +
  facet_grid(AnswerQUDRelevant~Mention)

# ggsave("graphs/denisty_QUDxMention_rawRT.pdf",width=6,height=3)


# Violn plot
ggplot(agr, aes(x=Conj, y=meanRT,fill=Conj,alpha=QUDType,color=Conj)) + 
  geom_violin(trim=FALSE,alpha=.4) +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  facet_grid(AnswerQUDRelevant~Mention)

# ggsave("../graphs/1a_violin.pdf",width=4,height=2)
```

```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  group_by(QUDType,Conj,AnswerQUDRelevant,Mention) %>%
  summarize(meanRT = mean(DecisionRT), CILow = ci.low(DecisionRT), CIHigh = ci.high(DecisionRT)) %>%
  mutate(YMin = meanRT - CILow, YMax = meanRT + CIHigh)

dodge <- position_dodge(.9)
ggplot(agr,aes(x=Conj, y=meanRT, fill=QUDType)) +
  facet_grid(Mention~AnswerQUDRelevant) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean RT for Decision RT")
```


## QUD x Negation (raw RT)
```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  # is.numeric(DecisionRT) %>%
  group_by(Letters,Conj,QUDType,Negation) %>% #,Mention
  summarize(meanRT = mean(DecisionRT)) 
  # mutate(YMin = meanLogRT - CILow, YMax = meanLogRT + CIHigh)

ggplot(agr, aes(x = meanRT, fill=Conj, color=Conj)) +
  geom_density(alpha = .4) +
  facet_grid(Negation~QUDType)

# ggsave("graphs/denisty_QUDxMention_rawRT.pdf",width=6,height=3)


# Violn plot
ggplot(agr, aes(x=Conj, y=meanRT,fill=Conj, color=Conj)) + 
  geom_violin(trim=FALSE,alpha=.4) +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  facet_grid(Negation~QUDType)

# ggsave("../graphs/1a_violin.pdf",width=4,height=2)
```


```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  group_by(QUDType,Conj,Negation) %>%
  summarize(meanRT = mean(DecisionRT), CILow = ci.low(DecisionRT), CIHigh = ci.high(DecisionRT)) %>%
  mutate(YMin = meanRT - CILow, YMax = meanRT + CIHigh)

dodge <- position_dodge(.9)
ggplot(agr,aes(x=Conj, y=meanRT, fill=QUDType)) +
  facet_wrap(~Negation) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean RT for Decision RT")
```

## QUD x Negqtion X AnswerQUDRelevant (raw RT)
```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  # is.numeric(DecisionRT) %>%
  group_by(Letters,Conj,QUDType,Negation,AnswerQUDRelevant) %>% #,Mention
  summarize(meanRT = mean(DecisionRT)) 
  # mutate(YMin = meanLogRT - CILow, YMax = meanLogRT + CIHigh)

ggplot(agr, aes(x = meanRT, fill=Conj, alpha=QUDType, color=Conj)) +
  geom_density(alpha = .4) +
  facet_grid(AnswerQUDRelevant~Negation)

# ggsave("graphs/denisty_QUDxMention_rawRT.pdf",width=6,height=3)


# Violn plot
ggplot(agr, aes(x=Conj, y=meanRT,fill=Conj,alpha=QUDType,color=Conj)) + 
  geom_violin(trim=FALSE,alpha=.4) +
  geom_jitter(shape=16, position=position_jitter(0.2)) +
  facet_grid(AnswerQUDRelevant~Negation)

# ggsave("../graphs/1a_violin.pdf",width=4,height=2)
```


```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  group_by(QUDType,Conj,AnswerQUDRelevant,Negation) %>%
  summarize(meanRT = mean(DecisionRT), CILow = ci.low(DecisionRT), CIHigh = ci.high(DecisionRT)) %>%
  mutate(YMin = meanRT - CILow, YMax = meanRT + CIHigh)

dodge <- position_dodge(.9)
ggplot(agr,aes(x=Conj, y=meanRT, fill=QUDType)) +
  facet_grid(Negation~AnswerQUDRelevant) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean RT for Decision RT")
```



# Looking at particular items

```{r, fig.width=6,fig.height=8}
d$Number <- as.factor(d$Number)
agr <- d %>%
  filter(Type =="critical") %>%
  group_by(Number,QUDType) %>%
  summarize(meanRT = mean(DecisionRT), CILow = ci.low(DecisionRT), CIHigh = ci.high(DecisionRT)) %>%
  mutate(YMin = meanRT - CILow, YMax = meanRT + CIHigh)
# View(agr)

dodge <- position_dodge(.9)
ggplot(agr,aes(x=QUDType, y=meanRT, fill=QUDType)) +
  facet_wrap(~Number,ncol=2) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge)
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  # ggtitle("mean RT for Decision RT")
```



```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  filter(Number %in% c("7","8","1","2")) %>%
  group_by(Number,QUDType) %>%
  summarize(meanRT = mean(DecisionRT), CILow = ci.low(DecisionRT), CIHigh = ci.high(DecisionRT)) %>%
  mutate(YMin = meanRT - CILow, YMax = meanRT + CIHigh)


dodge <- position_dodge(.9)
ggplot(agr,aes(x=Number, y=meanRT, fill=QUDType)) +
  # facet_wrap(~Number) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean RT for Decision RT, 7/8, 1/2")
```



troublesome cases:
1: EBT,LHN
2: TYK,IYG
7: JLP, XDS
8: QDR, UOP

irel rel
1: EBT 	"There is no cue, and there is a T"
1': LHN "There is no P and there is an H" <<< lower mean

2: TYK: "There is no L, but there is a K"
2': IYG "There is no X but there is an I"

rel rel
7: JLP "There is no U and there is a J"
7': XDS "There is no O and there is an X"

8: QDR "There is no V but there is a D"
8': UOP "There is no F but there is a U"
```{r, fig.width=10,fig.height=5}
agr <- d %>%
  filter(Type =="critical") %>%
  filter(Number %in% c("7","8","1","2")) %>%
  # is.numeric(DecisionRT) %>%
  group_by(QUDType,Letters) %>%
  summarize(meanRT_DecisionRT = mean(DecisionRT), CILow = ci.low(DecisionRT), CIHigh = ci.high(DecisionRT)) %>%
  mutate(YMin = meanRT_DecisionRT - CILow, YMax = meanRT_DecisionRT + CIHigh)


# reoder the levels so that we can see side-by-side the comparisons
agr$Letters <- factor(agr$Letters, levels=c("EBT","LHN","TYK","IYG","JLP","XDS","QDR","UOP"))

dodge <- position_dodge(.9)
ggplot(agr,aes(x=Letters, y=meanRT_DecisionRT,alpha=QUDType, fill=Letters)) +
  # facet_wrap(~QUDType, ncol=3) +
  # facet_wrap(~Wh, ncol=2) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean RT for Decision RT, individual trials in order 1, 2, 7, 8")
```


# The following items need to be all the same in NoQUD and General QUD

```{r, fig.width=6,fig.height=8}
# Look at the Decision RT reading time
agr <- d %>%
  filter(Type =="critical") %>%
  filter(Number %in% c("3","4","5","6","9","10","11","12")) %>%
  # is.numeric(DecisionRT) %>%
  group_by(QUDType,Number) %>%
  summarize(meanRT_DecisionRT = mean(DecisionRT), CILow = ci.low(DecisionRT), CIHigh = ci.high(DecisionRT)) %>%
  mutate(YMin = meanRT_DecisionRT - CILow, YMax = meanRT_DecisionRT + CIHigh)

# reoder the levels so that we can see side-by-side the comparisons
# df_DecisionRT$Letters <- factor(df_DecisionRT$Letters, levels=c("EBT","LHN","TYK","IYG","JLP","XDS","QDR","UOP"))

dodge <- position_dodge(.9)
ggplot(agr,aes(x=QUDType, y=meanRT_DecisionRT, fill=QUDType)) +
  facet_wrap(~Number, ncol=2) +
  # facet_wrap(~Wh, ncol=2) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean RT for Decision RT, individual trials in order 3-6, 9-12")
```



```{r, fig.width=5,fig.height=10}
# Look at the Decision RT reading time
agr <- d %>%
  filter(Type =="critical") %>%
  filter(Number %in% c("3","4","5","6","9","10","11","12")) %>%
  # is.numeric(DecisionRT) %>%
  group_by(QUDType,Letters) %>%
  summarize(meanRT_DecisionRT = mean(DecisionRT), CILow = ci.low(DecisionRT), CIHigh = ci.high(DecisionRT)) %>%
  mutate(YMin = meanRT_DecisionRT - CILow, YMax = meanRT_DecisionRT + CIHigh)

# reoder the levels so that we can see side-by-side the comparisons
agr$Letters <- factor(agr$Letters, levels=c(
   # 3/4
   "ZFW","MCR",
    # 3'/4'
    "BQG","DNF",
  
    # 5/6
    "VGW","PBN",
    # 5'/6'
    "OTY","JXO",
    
    # 9/10
    "FQA","RUI",
    # 9'/10'
    "AKT","NJV",
      
      # 11/12
    "XAV","CEH",
       # 11'/12'
    "ZDY","IFL"))

dodge <- position_dodge(.9)
ggplot(agr,aes(x=QUDType, y=meanRT_DecisionRT, fill=QUDType)) +
  facet_wrap(~Letters, ncol=2) +
  # facet_wrap(~Wh, ncol=2) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean RT for Decision RT, individual trials in order 3-6, 9-12")
```


```{r, fig.width=10,fig.height=5}
dodge <- position_dodge(.9)
ggplot(agr,aes(x=QUDType, y=meanRT_DecisionRT, fill=Letters)) +
  # facet_wrap(~Letters, ncol=2) +
  # facet_wrap(~Wh, ncol=2) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean RT for Decision RT, individual trials in order 3-6, 9-12")

```




# LogRTs
```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  # is.numeric(DecisionRT) %>%
  group_by(QUDType,Conj,AnswerQUDRelevant,Mention) %>%
  summarize(meanLogRT = mean(log(DecisionRT)), CILow = ci.low(log(DecisionRT)), CIHigh = ci.high(log(DecisionRT))) %>%
  mutate(YMin = meanLogRT - CILow, YMax = meanLogRT + CIHigh)


# View(df_DecisionRT)

dodge <- position_dodge(.9)
ggplot(agr,aes(x=Conj, y=meanLogRT, fill=QUDType)) +
  facet_grid(Mention~AnswerQUDRelevant) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge) +
  # scale_fill_manual(values=cbPalette) +
  # scale_color_manual(values=cbPalette) +
  ggtitle("mean logRT for Decision RT")
```


```{r}
agr <- d %>%
  filter(Type =="critical") %>%
  # is.numeric(DecisionRT) %>%
  group_by(Letters,Conj,QUDType) %>% #AnswerQUDRelevant,Mention,QUDType
  summarize(meanLogRT = mean(log(DecisionRT))) 
  # mutate(YMin = meanLogRT - CILow, YMax = meanLogRT + CIHigh)

ggplot(agr, aes(x = meanLogRT, fill=Conj, color=Conj)) +
  geom_density(alpha = .4) +
  facet_wrap(~QUDType)

# ggsave("graphs/denisty_QUD_logRT.pdf",width=7,height=2)
```
